---
title: 'Visualization: Histograms and Time Series'
author: Ben Kolbrich
date: '2017-09-29'
slug: visualization-histograms-and-time-series
categories:
  - data science
  - R
  - Rstudio
tags:
  - Lahman
  - histograms
  - timeseries
  - time series
  - bar graphs
---
##Data Visualization
Here, we will demonstrate two new types of visualizations. We will recognize these from high school and everyday life, but we may not know how to code them in R.

###Histograms

Let's attempt to do so now, using data from the Lahman database about the overall distribution of weight for MLB players.
```{r setup, include=FALSE} 
library(Lahman)
library(ggplot2)
library(sqldf)
options(warn=-1)
```

```{r}
query<-"Select weight from Master"
result<-sqldf(query)
```
That lets us store the weights in a variable, named 'result'. This information can then be retrieved and used to display a graph.

```{r}
ggplot()+
  geom_histogram(data=result, aes(x=weight), color="blue", bins=60, fill="orange")+
  ggtitle("Weight Distribution Among All MLB Players")
```

###Time Series
Our next example is to plot a variable against time. In this example, we will do it plotting Babe Ruth's homeruns over the course of his career.
```{r}
query<-"Select yearID, HR From Batting
where playerID='ruthba01'"
result1<-sqldf(query)
```

Note the single quotations on ruthba01, as it's a nonnumerical value. Now we can plot the data, and this time add connecting lines to fully understand the trends.

```{r}
ggplot()+
  geom_point(data=result1, aes(x=yearID, y=HR), size=2.5)+
  geom_line(data=result1, aes(x=yearID, y=HR))+
  ggtitle("Babe Ruth's Homeruns Throughout his Career")
```

